### 2024-03-28 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendere

>>>>

Some patterns are noticible. In future explorations, we should hope to reach
some interpretations and hopefully discuss them with local friends who
know something about this area.

This can be considered a first step in reproducing some of the methods
of the existing insightful articles cited above.

## Conclusion, for now

For now, we will stop here.

This has mostly been a demonstration of a few libraries and practices
which are central to the emerging Clojure platform for data and science.

We have also had a glance into a rich dataset which can provide fruitful
examples for our future explorations, demonstrating nontrivial
phenomena in space and in time.
